Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-16 patient-clinician-workshop/pccworkshop.tex

Fortunately, many of these sites have APIs that provide access to the raw sensor data, making it feasible to access and interpret captured data by way of these services.  We propose that these APIs be used to consolidate information from among all of the services corresponding to a patient's personal health devices, into a single reprsentation kept with their EHR.  In particular, grounding this activity data in a common taxonomy with associated description logic, like those provided for medical diagnoses and diseases through SNOWMED-CT \cite{stearns2001snomed} and ICD-10 \cite{world1993icd}, could enable these diaries to interpreted directly by clinical medical systems, such as primary care information management systems.

>>>>

Fortunately, many of these sites have APIs that provide access to the raw sensor data, making it feasible to access and interpret captured data.  We propose that these APIs be used to consolidate information from among all of the services corresponding to a patient's personal health devices, into a single reprsentation kept with their EHR.  In particular, grounding this activity data in a uniform, common taxonomy and description logic, like those provided for medical diagnoses and diseases through SNOWMED-CT \cite{stearns2001snomed} and ICD-10 \cite{world1993icd}, would enable these diaries to interpretable by future clinical medical systems, such as primary care information management systems.
